Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-20 article.tex
typo
updates

\section{History}
Molecules are composed of collections of atoms, and the units that make up an atom are electrons and the atomic nucleus. When we consider the
 atomic energy then we must take into account both electron-nuclei and electron-electron interactions. The molecular energy consists of interactions
 between multiple atoms, and interactions between electrons from different nuclei. Molecular energy can be pictured as a large
 package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.

Obviously, it demands massive computation to find out the package energy as it contains a huge amount of particles. Therefore, some approximations
 need to be made to simply our model, which necessitates the introduction of molecular mechanics.

@@

But what if we want to reduce the computational complexity? One solution is to reduce the number of water molecules simulated, which is feasible given
 the relative much larger size of the iron ball. To make up for the loss in number of molecules, the rest if the parameters can be adapted. Whereby we
can manipulate the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before.

The computation complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters
 and still generate acceptable solutions.

This process is known as renormalisation group, and the results that this model generates are called low energy effective theory, in which the system
 size is reduced but the results are still accurate.

@@

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
 in nature by using quantum systems. A prominent driving factor of the interest in and development of quantum computing is the aim to create quantum
 hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
 is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
 interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
 testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
 and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.

@@

Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
characteristic of various types of molecules and their interactions. Quantum computing shows promise to eliminate such errors whilst using a
larger number of qubits. However, these factors work against each other. If such a machine can be built, there would be more states and thus
information to manipulate whilst withstanding error. This could revolutionise applications such as pharmaceuticals where cures and treatments
 for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered. If (or when should I say) this is possible,
  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!
\section{Conclusion and outlook}
As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
   and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
   error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
    where classical techniques fail in solving traditionally intractable problems.

>>>>

\section{History}
Molecules are composed of collections of atoms, and the units that make up an atom are electrons and the atomic nucleus. When we consider the
 atomic energy then we must take into account both electron-nuclei and electron-electron interactions. The molecular energy consists of interactions
 between multiple atoms, and interactions between electrons from different nuclei. Molecular energy can be pictured as a large
 package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms. Obviously, it
 demands massive computation to find out the package energy as it contains a huge amount of particles. Therefore, some approximations need to be
  made to simply our model, which necessitates the introduction of molecular mechanics.

@@

But what if we want to reduce the computational complexity? One solution is to reduce the number of water molecules simulated, which is feasible given
 the relative much larger size of the iron ball. To make up for the loss in number of molecules, the rest if the parameters can be adapted. Whereby we
can manipulate the parameters and the simulation gives slightly different solutions, but the overall trend is still the same as before. The computation
 complexity can still be compressed. We can repeat the process of reducing the number of molecules and adjusting the parameters and still generate
  acceptable solutions. This process is known as renormalisation group, and the results that this model generates are called low energy effective
  theory, in which the system size is reduced but the results are still accurate.

@@

One of the reasons that developing new approaches to tackling electronic structure calculations is of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
 in nature by using quantum systems. A primary driving factor of the interest in and development of quantum computing is the aim to create quantum
 hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
 is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
 interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
 testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
 and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.

@@

Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
characteristic of various types of molecules and their interactions. Quantum computing shows promise to eliminate such errors whilst using a
larger number of qubits. However, these factors work against each other. If such a machine can be built, there would be more states and thus
information to manipulate whilst withstanding error. This could revolutionise applications such as pharmaceuticals where cures and treatments
 for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered. If (or when should I say) this is possible,
  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!

\section{Conclusion and outlook}
As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
   and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
   error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
    where classical techniques fail in solving traditionally intractable problems.
